Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-06-27 article.tex
Rewrite introduction

% Include a list of up to six keywords after the abstract
\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, flow measurement, microfluidic, flow system}

@@

Monitoring cerebral blood flow (CBF) is essential during neurosurgery as it provides surgeons with the critical information needed to guide life-saving interventions and is a valuable tool in mitigating post-operative complications \cite{Kirkness.2005}. As such, a clinical system that provides continuous CBF monitoring is highly desired. Laser speckle contrast imaging (LSCI) is a noninvasive, label-free, optical imaging technique based on coherent dynamic light scattering that has been widely implemented for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.

Due to its widespread adoption, LSCI instrument design and development is an active area of research with microfluidic studies commonly used to quantify controlled flow changes in well-defined channels. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}. This speed can be converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of 21 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.

A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor and lead screw in order to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. These systems use compressed air to push liquid from a pressure-regulated reservoir through the microfluidic device at constant flow rates. Integration with an inline flow measurement device allows for feedback loop control and the programming of specific flow rates rather than pressure levels.

One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}. Standard LSCI systems use a single camera exposure time, limiting sensitivity to a small range of flows. Additionally, instrumentation factors such as illumination variation and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making. An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}. MESI has been shown to be reliable for chronic imaging and to have high correlation with \textit{in vivo} absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons. By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.

In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regulated flow system. By understanding the associated uncertainty with each system, we can provide insight on the experimental design for a microfluidic study that aims to assess the hardware performance of an optical system, without fear that performance can be compromised due to flow-related noise. Quantifying this error allows us to accurately determine the true sensitivity to relative flow changes of a MESI system. \textcolor{red}{Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%.} The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.

>>>>

% Include a list of up to six keywords after the abstract
\keywords{laser speckle contrast imaging, multi-exposure speckle imaging, flow measurement, microfluidic, flow system}

@@

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

Due to its popularity, LSCI (and MESI) instrument development is an active area of research with microfluidic studies commonly used to characterize performance in controlled flow environments. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) substrate \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Arias-Cruz.2019}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, or epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el,Arias-Cruz.2019} or whole blood \cite{Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}. This speed can be converted to a volumetric flow rate using the cross-sectional area of the flow channel, which is then used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump flow control system.

Pressure-driven flow regulation systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate. In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device. Thermal mass flow sensors are commonly used to measure the low flow rates found in microfluidics. These sensors use heating and temperature-sensing elements to detect the magnitude and direction of flow and are factory-calibrated to measure absolute flow rates for various fluids. Integration of the flow sensor with a feedback loop allows for the programming of specific flow rates rather than pressure levels.

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that characterizing optical techniques with microfluidic studies requires highly-accurate flow control.
